
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}



\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingPosition}[2]{
  \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sasha Chepurnoi} & Email : \href{mailto:sasha.chepurnoii@gmail.com}{sasha.chepurnoii@gmail.com}\\
  \color{blue}
  \href{https://github.com/AChepurnoi}{Github} 
  \color{black}
  And 
  \color{blue}  
  \href{https://www.linkedin.com/in/sasha-chepurnoii/}{Linkedin} & Mobile : +380668054000
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://uptech.team}{Uptech}}{Kyiv}
      {Backend Engineer}{Jun 2016 - Present}

      \resumeSubheadingPosition
      {Backend Lead}{Feb 2018 - October 2019}
      \resumeItemListStart
        \resumeItem{Company wide}
          {As Backend lead, was responsible for alignment of the backend team of 8 people with company strategy and vision, cross-department collaboration.
          Implemented personal development plans with the team members, knowledge sharing talks, one-on-ones, and OKR framework.
          Helped team with a cloud configuration, system design, recruiting, soft and hard skills growth. Participated in knowledge sharing events (Tech Talks), pre-sale calls. 
          Also participated in technical discovery for different projects to define solution architecture, tech stack, and estimate
          }
        \resumeItem{Yaza}
         {Designed an API for a map-based messenger with a focus on video content using Java, Spring Boot 2 and clean architecture approach (Hexagonal architecture).
         Implemented efficient storage for big amount of video content and HLS encrypted video streaming using Amazon S3, CloudFront and Mongodb,
         secure uploading and permission management. 
         Integrated Google Maps for searching and suggesting places, PubNub for fast and reliable real-time messaging. 
         Implemented CI/CD process using Travis CI, cloud/configuration management with Terraform and Ansible,
         deployment on ECS cluster with Docker.
         
         }
         \resumeItem{Advaice}
          {Designed an API for advertising platform. 
          Integrated collection of advertising data from Google Adwords, Facebook Ads, MyTarget Ads and event data from Appsflyer and Adjust.
          Implemented rich report generation, billing system using Stripe API and emailing using Mailchimp API. 
          Created Python Lambda functions to parse Apple Appstore/Google play. 
          Lead team of 4 people. 
          Implemented CI/CD process using Travis CI, cloud/configuration management with Terraform and Ansible.
          }

          \resumeItem{Rivalz}
        {Designed and implemented an API for mobile application. 
        Implemented App store and Google play in-app purchases verification, 
        Stripe payment API integration, notifications using Firebase API. 
        Integrated scheduling system using Google Calendar API.
        Lead team of 2 developers.
        Implemented CI/CD process using Jenkins, cloud/configuration management with Terraform and Ansible.
        }
        
        \resumeItem{Vitalacy}
        {Implemented an API with Kotlin and Spring Boot framework for the healthcare IOT platform. 
        Implemented efficient background batch data processing. 
        Integrated room management system with PostGIS extension for PostgreSQL. 
        Implemented a reliable permission management system for different roles. 
        Configured a Jenkins CI to run tests and do deployment on AWS Beanstalk
        }
      \resumeItemListEnd

    \resumeSubheading
      {Bionic Development Studio}{Kyiv}
      {Junior Java Developer}{Dec 2015 - Jun 2016}
      \resumeItemListStart
        \resumeItem{Driver management system}
          {
            Implemented domain-specific calculations and excel report generation with Jasper Reports.
            Tuned Hibernate queries and increased the overall performance of the application
            Developed an API for Android client.
            Implemented Android application as a frontend for API
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Kidney Tumor Segmentation Challenge}
      {Implemented segmentation of 3D CT scan of kidney and kidney tumor. Trained a robust 3D Unet model using PyTorch on sparse high dimensional data }
    \resumeSubItem{Kaggle Airbus Ship Segmentation}
      {Top 10\% result(80 place) in Ships Segmentation Challenge. Implemented and trained an Unet-like neural network with data augmentation and multistep learning process}
    \resumeSubItem{Kaggle Salt Identification}
      {Top 8\% result in Salt Segmentation Challenge. Implemented and trained UNet with Deep supervision, attention and cyclic learning rate. Built a pipeline with strong data augmentation, validation and evaluation.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Ukrainian Catholic University}{Lviv}
    {Master of Science in Data Science and Machine Learning}{Sep. 2018 -- Jan. 2020}
  \resumeSubheading
    {Igor Sikorsky Kyiv Polytechnic Institute}{Kyiv}
    {Bachelor of Software Engineering}{Sep. 2014 -- July. 2018}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}